---
title: "Metaanalysis_exercise"
author: "Gunneet Singh"
date: "5/26/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(meta)
library(metafor)
library(dplyr)
```



```{r}
# Importing the dataset
data <- read_excel("metaanalysis_data.xlsx")
```

### Case 1. Our effect sizes are already calculated


```{r}
m <- metagen(TE=N_boys,
             seTE=Mean_boys_play_male,
             data=data,
             studlab=paste(Study),
             comb.fixed = TRUE,
             comb.random = FALSE)
m
```


### Case 2. Our effect sizes are not calculated but we have the necessary data


```{r}
m.raw <- metacont(n.e=N_boys,
                  mean.e=Mean_boys_play_male,
                  sd.e=SD_boys_play_male,
                  n.c=N_girls,
                  mean.c=Mean_girls_play_male,
                  sd.c=SD_girls_play_male,
                  data=data,
                  studlab=paste(Study),
                  comb.fixed = TRUE,
                  comb.random = TRUE,
)
m.raw
```

### Case 3. `matada` again but with Random effects

```{r}
m_re <- metagen(TE=N_boys,
             seTE=Mean_boys_play_male,
             data=data,
             studlab=paste(Study),
             comb.fixed = FALSE,
             comb.random = TRUE)
m_re
```

### One popular way of depicting such analyses: `forest plots`

With `meta` package this is very simple. We just put our results into the `forest()` function:

```{r}
m %>% forest(sortvar=TE)
```

```{r}
m_re %>% forest(sortvar=TE)
```


## Checking for publication bias

Again, we use what we defined previously.

```{r}
m %>% funnel()
```

And we can add some additional features, e.g. let's make it a 'contour-enhanced' funnel plot:

```{r}
m %>% funnel(contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))+
legend(1.4, 0, c("p < 0.05", "p<0.025", "< 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```
